Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-02-10 AO_bondedSi.tex
add some text about the sample transport accessory, realization about coarse mesh comparable to beam size

>>>>

\subsection{Spatially resolved measurements with Sample Transport Accessory}
We acquired spatially resolved measurements of sample VG09-12 with the Cary 5000 sample transport accessory.  This accessory translates the sample through the measurement beam and takes a transmission spectrum at each position.  The 2 mm step size is comparable to the monochromator's slit size.  We sampled 50 mm across the mesh pattern and into the off-mesh pattern.  Figure \verb|\ref{photo-of-VG09-12}| shows an illustration of sample VG09-12, with the approximate center locations of measurements marked with black dots.  The colored dots match the color of the spectra in Figure \verb|\ref{fig-STA-obs}| The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a lab measured depth of $49\pm6\;$nm, and fill factor of 50\%.  The prediction band for a transmision spectrum with those properties, and zero extra gap is shown as the green apple colored swath.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \verb|\ref{fig-STA-obs}|.  Instead we see that some spectra are inside the swath, and others show a deficit of flux, indicating an extra gap as in the mixture model in Equation \verb|\ref{mixture-model-equation}|.
